XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-27 talk/icooolps2011/paper.tex
Finish renaming 'version number' into 'version object'.

XXX should we say ``version number'' all around when it is really an object?

@@

What is interesting here is that \texttt{\_find\_method} takes the \texttt{version}
argument but it does not use it at all. Its only purpose is to make the call
pure, because when the version number changes, the result of the call might be
different than the previous one.

>>>>

@@

What is interesting here is that \texttt{\_find\_method} takes the \texttt{version}
argument but it does not use it at all. Its only purpose is to make the call
pure, because when the version object changes, the result of the call might be
different than the previous one.
